Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-22 docs/manuscript/manuscript.tex
Edit of labels for the table.

\begin{table}[h!]
  \centering
  \begin{tabular}{p{1in} p{3in} p{2in}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{imws} & Households using an improved water source
 & Percentage of households whose main source of drinking water is an improved source.
 \\\midrule
  \texttt{pipy} & Households using water piped into yard/plot
& Percentage of households whose main source of drinking water is water piped into the yard or plot.
\\\midrule
 \texttt{truc} & Households using tanker truck & Percentage of households whose main source of drinking water is tanker truck.
\\\midrule
 \texttt{ctan} & Households using cart with tank & Percentage of households whose main source of drinking water is cart with tank.
\\\midrule
 \texttt{bott} & Households using bottled water & Percentage of households whose main source of drinking water is bottled water/demi john.
\\\midrule
 \texttt{uiws} & Households using an unimproved water source & Percentage of households whose main source of drinking water is an unimproved source.
\\\midrule
 \texttt{othw} & Households using other water source & Percentage of households whose main source of drinking water is other.
\\\midrule
 \texttt{iwsp} & Households with improved water source on the premises & Percentage of the de jure population living in households with an improved water source on the premises.
\\\midrule
 \texttt{basw} & Households with basic water service
 & Percentage of households with basic water service, defined as an improved water source with either water on the premises or round-trip collection time is 30 minutes or less.
\\\midrule
 \texttt{liws} & Households with limited water service
 & Percentage of households with limited water service, defined as an improved water source with round-trip collection time greater than 30 minutes.
\\\midrule
 \texttt{prem} & Households with water on the premises
 & Percentage of households with water on the premises.
\\\midrule
 \texttt{bicy} & Households possessing a bicycle
 & Percentage of households possessing a bicycle.
\\\midrule
 \texttt{acar} & Households possessing an animal drawn cart
 & Percentage of households possessing an animal drawn cart.
\\\midrule
 \texttt{mcyc} & Households possessing a motorcycle
 & Percentage of households possessing a motorcycle.
\\\midrule
 \texttt{pcar} & Households possessing a private car
 & Percentage of households possessing a private car.
\\\midrule
 \texttt{boat} & Households possessing a boat with a motor
 & Percentage of households possessing a boat with a motor.
\\\midrule
 \texttt{wigc} & Wealth index Gini coefficient
 & The Gini coefficient indicates the level of concentration of wealth in the country.
\\\midrule
 & \\\bottomrule
  \end{tabular}
  \caption{Summary of explanatory variables (national averages measured as percentage at household level)}
  \label{tab:summary-var}
\end{table}
 \subsection*{Summary of variables}
\hl{Here, you show and discuss the data distributions (e.g. histograms, correlation plots, etc)}

>>>>

\begin{table}[h!]
  \centering
  \begin{tabular}{p{1in} p{3in} p{2in}}\toprule
    \bf Variable & \bf Description & \bf Definition \\\midrule
    \texttt{imws} & Improved water source
 & Drinking water is an improved source.
 \\\midrule
  \texttt{pipy} & Water piped into yard/plot
& Drinking water is water piped into the yard or plot.
\\\midrule
 \texttt{truc} & Tanker truck & Drinking water is tanker truck.
\\\midrule
 \texttt{ctan} & Cart with tank & Drinking water is cart with tank.
\\\midrule
 \texttt{bott} & Bottled water & Drinking water is bottled water/demi john.
\\\midrule
 \texttt{uiws} & Unimproved water source & Drinking water is an unimproved source.
\\\midrule
 \texttt{othw} & Other water source & Drinking water is other.
\\\midrule
 \texttt{iwsp} & Improved water source on the premises & The de jure population living in households with an improved water source on the premises.
\\\midrule
 \texttt{basw} & Basic water service
 & Defined as an improved water source with either water on the premises or round-trip collection time is 30 minutes or less.
\\\midrule
 \texttt{liws} & Households with limited water service
 & Percentage of households with limited water service, defined as an improved water source with round-trip collection time greater than 30 minutes.
\\\midrule
 \texttt{prem} & Households with water on the premises
 & Percentage of households with water on the premises.
\\\midrule
 \texttt{bicy} & Households possessing a bicycle
 & Percentage of households possessing a bicycle.
\\\midrule
 \texttt{acar} & Households possessing an animal drawn cart
 & Percentage of households possessing an animal drawn cart.
\\\midrule
 \texttt{mcyc} & Households possessing a motorcycle
 & Percentage of households possessing a motorcycle.
\\\midrule
 \texttt{pcar} & Households possessing a private car
 & Percentage of households possessing a private car.
\\\midrule
 \texttt{boat} & Households possessing a boat with a motor
 & Percentage of households possessing a boat with a motor.
\\\midrule
 \texttt{wigc} & Wealth index Gini coefficient
 & The Gini coefficient indicates the level of concentration of wealth in the country.
\\\midrule
 & \\\bottomrule
  \end{tabular}
  \caption{Summary of explanatory variables (National Household usage Averages measured as percentage for Main Source)}
  \label{tab:summary-var}
\end{table}
 \subsection*{Summary of variables}
\hl{Here, you show and discuss the data distributions (e.g. histograms, correlation plots, etc)}
